Finite Property Convex Elicitation Notes

### 2018-08-13 cvx-fin-notes.tex
notes from meeting with bo

>>>>

\raf{NOTES from call w/ Bo on 8/13/2018:}
\begin{itemize}
\item We would like a very strong link function, which takes any report in the convex domain, and returns the \emph{full set} of optimal reports, of the original finite property, but this is too strong -- consider abstain and the line segment connecting corner and center vs corner, center, and opposite corner.
So we should at least show the weaker link function that takes any report in the convex domain and returns \emph{some} optimal report of the original property.
\item We can probably prove that if $L$ essentially elicits a finite property, then $L$ is FPLC on the convex hull of the embedded reports.
\end{itemize}
